\thetitle

### 2021-03-03 writing/rational-experiment.tex
'the experiment' does _not_ 'do'

Trails and their properties provide the tools for a rigorous examination of
blame for Natural, Transient and Erasure. In line with the discussion so far,
the experiment collects data to answer three initial questions for 
interesting debugging scenarios:
\begin{itemize}
\item[$Q_1$] Is blame useful in the context of Natural?

@@

In detail, the answer to $Q_1$ demands a comparison of the success of the Natural
blame and Natural exception trails for all debugging scenarios.  The
first step is to construct each mutant's scenario lattice and identify their
debugging scenarios.  The experiment then extends the trails that start
from those roots according to the Natural-blame programmer.  If no scenarios can
be added to the trail, the experiment checks whether the last scenario
of the trail type-checks or not. If it does, the
Natural-blame trail is successful; otherwise it is failing. 
Figure~\ref{fig:process} summarizes this experimental process for
one mode of the rational programmer and connects it with the mutations from
section~\ref{sec:mutate}.
The experiment repeats the process for the same roots with the other mode, Natural
exceptions.
After completing, the experiment
reports the success/failure results of the trails to determine the proportion of
scenarios where Natural blame is more useful than Natural exceptions.  Question
$Q_1$ has a positive answer if a root exists where the above is true because it
is evidence that there is at least one interesting scenario that the rational
programmer manages to debug because of blame information.  The process is analogous
for $Q_2$ and $Q_3$, using the respective modes of the rational programmer.

>>>>

Trails and their properties provide the tools for a rigorous examination of
blame for Natural, Transient and Erasure. In line with the discussion so far,
the test bed collects data to answer three initial questions for 
interesting debugging scenarios:
\begin{itemize}
\item[$Q_1$] Is blame useful in the context of Natural?

@@

In detail, the answer to $Q_1$ demands a comparison of the success of the Natural
blame and Natural exception trails for all debugging scenarios.  The
first step is to construct each mutant's scenario lattice and identify their
debugging scenarios.  The test bed then extends the trails that start
from those roots according to the Natural-blame programmer.  If no scenarios can
be added to the trail, the test bed checks whether the last scenario
of the trail type-checks or not. If it does, the
Natural-blame trail is successful; otherwise it is failing. 
Figure~\ref{fig:process} summarizes this experimental process for
one mode of the rational programmer and connects it with the mutations from
section~\ref{sec:mutate}.
The process is repeated for the same roots with the other mode, Natural
exceptions.
After completing, the test bed
reports the success/failure results of the trails to determine the proportion of
scenarios where Natural blame is more useful than Natural exceptions.  Question
$Q_1$ has a positive answer if a root exists where the above is true because it
is evidence that there is at least one interesting scenario that the rational
programmer manages to debug because of blame information.  The process is analogous
for $Q_2$ and $Q_3$, using the respective modes of the rational programmer.
